Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

>>>>

asymptomaticQ2_2 = asymptomaticQ2_2 %>% filter(!(q3_pp_m=="" & is.na(q3_pa_m)))
asymptomaticQ2_2$q3_setting=ifelse(asymptomaticQ2_2$q3_setting=="",NA,asymptomaticQ2_2$q3_setting)

s <- strsplit(asymptomaticQ2_2$q3_setting, split = ";")
pp_m <- strsplit(asymptomaticQ2_2$q3_pp_m, split = ";")
pp_l <- strsplit(asymptomaticQ2_2$q3_pp_l, split = ";")
pp_u <- strsplit(asymptomaticQ2_2$q3_pp_u, split = ";")

dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ2_2$author_1), sapply(pp_m, length)),
                 Q3set=unlist(s),
                 p = as.numeric(unlist(pp_m)), 
                 l = as.numeric(unlist(pp_l)),
                 h = as.numeric(unlist(pp_u)),
                 setting="Pre-symptomatic",stringsAsFactors = FALSE)

dfQ3a[dfQ3a==9999]<-NA
dfQ3a=dfQ3a[!is.na(dfQ3a$p),]

dfQ3b=data.frame(label=paste0("   ",asymptomaticQ2_2$author_1),
                 Q3set=NA,
                 p = asymptomaticQ2_2$q3_pa_m, 
                 l = asymptomaticQ2_2$q3_pa_l,
                 h = asymptomaticQ2_2$q3_pa_u,
                 setting="Asymptomatic",stringsAsFactors = FALSE)

dfQ3b[dfQ3b==9999]<-NA
dfQ3b=dfQ3b[!is.na(dfQ3b$p),]

dfQ3=rbind.data.frame(dfQ3b,dfQ3a, stringsAsFactors = FALSE)

dfQ3$line=1:nrow(dfQ3)
dfQ3$type=rep(2,nrow(dfQ3))

insertRow <- function(existingDF, newrow, r) {
  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
  existingDF[r,] <- newrow
  existingDF
}

dfQ3=insertRow(dfQ3,c("Asymptomatic transmission",NA,NA,NA,NA,NA,1,1),1)

dfQ3=insertRow(dfQ3,c("Pre-symptomatic transmission",NA,NA,NA,NA,NA,1,1),nrow(dfQ3b)+2)
dfQ3=insertRow(dfQ3,c(rep(NA,7),1),nrow(dfQ3b)+2)
dfQ3$line=1:nrow(dfQ3)

dfQ3$p=as.numeric(dfQ3$p)
dfQ3$l=as.numeric(dfQ3$l)
dfQ3$h=as.numeric(dfQ3$h)

# dfQ3c<-read.csv(file="Q3.csv", stringsAsFactors = FALSE)
# dfQ3$p=dfQ3$p/100
# dfQ3$l=dfQ3$l/100
# dfQ3$h=dfQ3$h/100

dataG=dfQ3

dig=2
r<-function(x){format(round(as.numeric(x),2),dig=2)}

dataG$label=ifelse(dataG$type==2,
                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)

dataG$fontface=ifelse(dataG$type==1, "italic","plain")

dataG$label_studyCI=ifelse(!is.na(dataG$h), paste0("[",r(dataG$l),";",r(dataG$h),"]"),NA)
dataG$label_study=ifelse(!is.na(dataG$p),r(dataG$p),NA)

p=ggplot()+ 
  geom_point(data=dataG,aes(y=dataG$line, x=dataG$p),fill="gray", shape=22, color="black",size=4)+
  geom_errorbarh(data=dataG,aes(y=dataG$line, xmin=dataG$l, xmax=dataG$h), height=0.3)+

  geom_text(aes(y=c(-1,-1,-1), x=c(-2,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+

  geom_text(data=dataG,aes(y=dataG$line, x=1.25, label=label_study), hjust = 0)+
  geom_text(data=dataG,aes(y=dataG$line, x=1.75, label=label_studyCI), hjust = 0)+

  geom_text(data=dataG,aes(y=dataG$line, x=-2, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
  #geom_rect(data=dataG,aes(xmin=dataG$Pl,xmax=dataG$Ph,ymin=dataG$line-0.1,ymax=dataG$line+0.1),color="black", fill="red")+
  theme_void() + 
  scale_y_reverse()+
  geom_segment(aes(y=max(dataG$line)+1, x=0, xend=1, yend=max(dataG$line)+1))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0,xend=0))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.25,xend=0.25))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.5,xend=0.5))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.75,xend=0.75))+
  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=1,xend=1))+
  geom_text(aes(y=rep(max(dataG$line)+2,5),x=0:4/4, label=c(0.00,0.25,0.5,0.75,1.00)))+
  #geom_segment(data=dataG,aes(x=vlineloc, xend=vlineloc, y=0, yend=max(dataG$line)+1), linetype=3)+

  xlim(c(-2,2.5))+
  theme(legend.position = "none")
